### 2023-05-30 docs/minutes/slides_25_05/document.tex
corrected sigma_p prior
loosen priors on f and fdot
bayes ratio at large scale
V5 Bayes run

	\begin{itemize}
		\item Earth terms model $g'(\tau; \bar{\theta}) = 1 - \frac{1}{2} \frac{ H_{ij}q^i q^j }{(1 + \bar{n}\cdot \bar{q}) } \left[ \cos(-\Omega \tau +\Phi_0) \right]$
		\item Zero process noise  $\sigma_p = 0$
		\item No heterodyning
		\item Single noise realisation
    \end{itemize}

@@

	\begin{itemize}
		\item Earth terms model 
		\item \alert{Non - Zero process noise  $\sigma_p \neq 0$}
		\item \alert{Heterodyning}
		\item \alert{Multiple noise realisations}
	\end{itemize}

@@

	$f_{\rm EM}$ is the exact, true solution parametrised by the unknowns $f_0, \dot{f}_0$. This heterodyning is just a change of variables

@@

>>>>

	\begin{itemize}
		\item Earth terms model $g'(\tau; \bar{\theta}) = 1 - \frac{1}{2} \frac{ H_{ij}q^i q^j }{(1 + \bar{n}\cdot \bar{q}) } \left[ \cos(-\Omega \tau +\Phi_0) \right]$
		\item Zero process noise  $\sigma_p = 0$
		\item No heterodyning
		\item Single noise realisation
		\item Single set of parameters realisation
    \end{itemize}

@@

	\begin{itemize}
		\item Earth terms model 
		\item \alert{Non - zero process noise  $\sigma_p \neq 0$} $\checkmark$
		\item \alert{Heterodyning} $\checkmark$
		\item \alert{Multiple noise realisations} $\checkmark$
		\item Single set of parameters realisation
	\end{itemize}

@@

	$f_{\rm EM}$ is the exact, true solution parametrised by the unknowns $f_0, \dot{f}_0$. This ``heterodyning" is just a change of variables

@@

	For our case where we have synthetic data we can set $f_{\rm EM} = f^{\, *}_{\rm EM}$. In the general ``real-world" case we cannot - but this is just a scaling, not a  fundamental structure viz. d.o.f

	\begin{frame}[label={first_slide}]

	\includegraphics[width=0.85\textwidth,height=0.85\textwidth]{images/1237_broad_GW}
		\only<1>{%
		\tikz[overlay,remember picture]
		\node[fill=white,text=black] at ([xshift=1.5cm,yshift=3.5cm]current page.center){$h = 10^{-12}$, $\sigma_p = \mathcal{U}(10^{-21}, 10^{-19})$};
	}
	\only<1>{%
	\tikz[overlay,remember picture]
	\node[fill=white,text=black] at ([xshift=1.5cm,yshift=3.0cm]current page.center){Heterodyned equations, Full PTA};

}
	\only<1>{%
	\tikz[overlay,remember picture]
	\node[fill=white,text=black] at ([xshift=1.5cm,yshift=2.5cm]current page.center){$\bar{\theta}_{\rm GW}$, c.f. Slide \ref{first_slide_noise}};

	\includegraphics[width=0.85\textwidth,height=0.85\textwidth]{images/1237_broad_f}

		\only<1>{%
		\tikz[overlay,remember picture]
		\node[fill=white,text=black] at ([xshift=1.5cm,yshift=3.5cm]current page.center){Slightly deceptive: very tight priors - to discuss};
	}

	\includegraphics[width=0.85\textwidth,height=0.85\textwidth]{images/1237_broad_fdot}

	\only<1>{%
		\tikz[overlay,remember picture]
		\node[fill=white,text=black] at ([xshift=1.5cm,yshift=3.5cm]current page.center){Slightly deceptive: very tight priors - to discuss};
	}

	\includegraphics[width=0.85\textwidth,height=0.85\textwidth]{images/1237_broad_sigma_p}

	\only<1>{%
		\tikz[overlay,remember picture]
		\node[fill=white,text=black] at ([xshift=1.5cm,yshift=3.5cm]current page.center){LogUniform prior};
	}
		\only<1>{%
		\tikz[overlay,remember picture]
		\node[fill=white,text=black] at ([xshift=1.5cm,yshift=3.0cm]current page.center){Bad: not super accurate};

	}
		\only<1>{%
	\tikz[overlay,remember picture]
	\node[fill=white,text=black] at ([xshift=1.9cm,yshift=2.5cm]current page.center){Good: does not impact estimates of $\bar{\theta}_{\rm GW}$};

%\begin{frame}{}
%	
%	
%	\includegraphics[width=0.85\textwidth,height=0.85\textwidth]{images/1237_broad_sigma_p}
%	
%	\only<1>{%
%		\tikz[overlay,remember picture]
%		\node[fill=white,text=black] at ([xshift=1.5cm,yshift=3.5cm]current page.center){LogUniform prior};
%	}
%\end{frame}

\begin{frame}
	But what about different realisations of a) measurement noise and b) process noise?

	\begin{frame}[label={first_slide_noise}]

	\includegraphics[width=0.85\textwidth,height=0.85\textwidth]{images/stacked_GW_plot}
	\only<1>{%
		\tikz[overlay,remember picture]
		\node[fill=white,text=black] at ([xshift=1.5cm,yshift=3.5cm]current page.center){As Slide \ref{first_slide}, 5 noise realisations};
	}

	\begin{frame}

	\includegraphics[width=0.85\textwidth,height=0.85\textwidth]{images/stacked_f_plot}

	\begin{frame}

	\includegraphics[width=0.85\textwidth,height=0.85\textwidth]{images/stacked_fdto_plot}

	\begin{frame}

	\includegraphics[width=0.85\textwidth,height=0.85\textwidth]{images/stacked_sgima_p_plot}

\begin{frame}
	How about 100 noise realisations? 
\end{frame}

	\begin{frame}

	\includegraphics[width=0.32\textwidth,height=0.85\textwidth]{images/parameter_medians}
	\includegraphics[width=0.32\textwidth,height=0.85\textwidth]{images/parameter_medians_f}
	\includegraphics[width=0.32\textwidth,height=0.85\textwidth]{images/parameter_medians_fdot}

	\begin{frame}	
	\centering
	\includegraphics[width=0.34\textwidth,height=0.85\textwidth]{images/parameter_medians_sigma_p}
\end{frame}

\begin{frame}
	Case examples - iota, h 
\end{frame}

\begin{frame}{Bayes ratios}

\includegraphics[width=0.85\textwidth,height=0.85\textwidth]{images/BayesRatioPlot}
